Topological Equivariant Artist Model

### 2022-02-28 slides/main.tex
decomposing nu

                \item[Locally Trivial] {for every point $\dbasepointc \in \dbasec$, there exists an open neighborhood $\dbasepointc \in \opensetc \subseteq \dbasec$ s.t. there is a homeomorphism $\pi^{-1}(\opensetc)\xrightarrow{\varphi} \opensetc \times \dfiberc$}

@@

    \onslide*<0|handout:3>{
        \begin{equation*}
    \begin{tikzcd}[ampersand replacement =\&]
    \cgamma{\opensetgc_1}{\dtotalpullc\restriction_{\opensetgc_1}} 
    \arrow[dd, "\iota^*"', hook, color=set] 
    \arrow[rrrr, "\vartistc_{\opensetgc_1}", bend left, color=artist, Rightarrow] \&  \& 
    \opensetgc_1 
    \arrow[ll, "\sheafc_{\gbasec, \dtotalpullc}", color=sheaf, maps to] 
    \arrow[rr, "\sheafc_{\gbasec,\gtotalc}"', color=sheaf, maps to] \&  \& 
    \cgamma{\opensetgc_1}{\gtotalc\restriction_{\opensetgc_1}} 
    \arrow[dd, "\iota^*", hook', color=set] \\
    {} 
    \arrow[rrrr, dotted, color=artist, Rightarrow] \&\&\&\& {} \\
    \cgamma{\opensetgc_2}{\dtotalpullc\restriction_{\opensetgc_2}} 
    \arrow[rrrr, "\vartistc_{\opensetgc_2}"', bend right, color=artist, Rightarrow] \&  \& 
    \opensetgc_2 
    \arrow[ll, "\sheafc_{\gbasec,\dtotalpullc}"', color=sheaf, maps to] 
    \arrow[rr, "\sheafc_{\gbasec, \gtotalc}", color=sheaf, maps to] 
    \arrow[uu, "\iota" description, hook, color=base] \& \& 
    \cgamma{\opensetgc_2}{\gtotalc\restriction_{\opensetgc_2}}   
    \end{tikzcd}
        \end{equation*}}    
    \onslide<0|handout:1>{
        \begin{equation*}
        \textcolor{nattran}{Nat}_{\opensetgc}(\textcolor{functor}{\vindexpull}\sheafc_{\dbasec, \dtotalc}, \sheafc_{\gbasec, \gtotalc}) = 
    \textcolor{nattran}{Nat}_{\opensetc}(\sheafc_{\dbasec, \dtotalc}, \textcolor{functor}{\vindexpush}\sheafc_{\gbasec, \gtotalc})
        \end{equation*}
    }
    \onslide<0|handout:4>{
        \begin{alertblock}{pull data section \dsectionc\ over graphic space $\gbasepointc \in \gbasec$}
            \begin{equation*}
                \vindexpullc\dsectionc(\gbasepointc) = \dsectionc(\vindexc(\gbasepointc)) = \dsectionc(\dbasepointc)
            \end{equation*}
        \end{alertblock}
        \begin{alertblock}{push graphic \gsectionc\ section over data space $\dbasepointc \in \dbasec$}
            \begin{equation*}
                \vindexpushc\gsectionc(\dbasepointc) = \gsectionc\restriction_{\vindexpre(\dbasepointc)} = \gsectionc(\gbasepointc) \forall \gbasepointc \in \vindexpre(\dbasepointc)
            \end{equation*}
        \end{alertblock}
        }
\end{frame}

@@

\subsection{Equivariance}
\begin{frame}{Transform Data}
    \begin{block}{Fiber Bundle Category}
        \begin{description}[style=newline]
            \item[object] $\dfiberc \hookrightarrow \dtotalc \xrightarrow{\pi} \dbasec$
            \item[morphisms] $\dfuncc: \dtotalc \rightarrow \dtotalc$ 
        \end{description}
    \end{block}
    \begin{block}{Fiber Category}
        The fiber $\dfiberc$ is the sole object of an arbitrary category $\mathcal{C}$.
        The morphisms on the fiber are $Hom(\dfiberc, \dfiberc)$
    \end{block}

@@

\begin{frame}{Checking if \vartistc\ is equivariant}
    \begin{equation*}
        \begin{tikzcd}[ampersand replacement=\&, row sep=huge]
            \cgamma{\opensetc}{\dtotalc\restriction_{\opensetc}} 
            \arrow[rr, "\vartistc", Rightarrow, color=artist] \&  \& 
            \cgamma{\opensetgc}{\gtotalc\restriction_{\opensetgc}} 
            \arrow[rrd, "\delta"'] 
            \arrow[rr, "render"] \&  \& visualization 
            \arrow[d, "measure" description] \\ 
            \&  \&  \&  \& M
            \end{tikzcd}
    \end{equation*}
\end{frame}

@@

\begin{frame}{Data to Visual Transformation: $\vchannelc: \dsectionc \mapsto \vsectionc$}
    \begin{equation*}
        \begin{tikzcd}[ampersand replacement=\&, row sep=huge]
            \cgamma{\opensetc}{\dtotalc\restriction_{\opensetc}} 
            \arrow[rr, "\vchannelc", color=artist, maps to] \& \& 
            \cgamma{\opensetc}{\vtotalc\restriction_{\opensetc}} \\
             \& \opensetc 
             \arrow[lu, "{\sheafc_{\dbasec,\dtotalc}}" description, maps to, color=sheaf] 
             \arrow[ru, "{\sheafc_{\dbasec, \vtotalc}}" description, maps to, color=sheaf] \& 
            \end{tikzcd}
    \end{equation*}

    \begin{alertblock}{constraints} 
        \begin{description}
            \item[equivariance] $\vchannelc(\dfuncc_{\dtotalc}(\dsectionc(\dbasepointc))) = \dfuncc_{\vtotalc}(\vchannelc(\dsectionc(\dbasepointc)))$, for all $\dbasepointc \in \dbasec$ 
            \item[continuity] $\lim\limits_{x\to \dbasepointc}(\vchannelc(\dsectionc(x))) = \vchannelc(\dsectionc(\dbasepointc))$ for all $\dbasepointc \in \dbasec$
            \item[pointwise] $\vchannelc: \dsectionc(\dbasepointc) \mapsto \vsectionc(\dbasepointc) = \vchannelc: \vindexpullc\dsectionc(\gbasepointc) \mapsto \vindexpullc\vsectionc(\gbasepointc)$ when $\vindexc(\gbasepointc) = \dbasepointc$ 
    \end{description} 
\end{alertblock}
\end{frame}

\begin{frame}{Functor $\vchannelc: \dsectionc \mapsto \vsectionc$}
    \begin{equation*}
        \begin{tikzcd}[ampersand replacement=\&, row sep=huge]
            \cgamma{\opensetc}{\dtotalc\restriction_{\opensetc}}
            \arrow[rr, "\vchannelc_{\dfiberc,\vfiberc}", maps to, color=artist] 
            \arrow[rrdd, "{\vchannelc_{\dfiberc,{\vfiberc}^{\prime}}}"', dotted, maps to, color=artist] 
            \&  \& 
            \cgamma{\opensetc}{\vtotalc\restriction_{\opensetc}} \coloneqq \cgamma{\opensetc}{\dtotalc^{\prime}\restriction_{\opensetc}} 
            \arrow[dd, "\vchannelc_{{\dfiberc}^{\prime}, {\vfiberc}^{\prime}}", maps to, color=artist] \\
            \&  \& \\
            \&  \& \cgamma{\opensetgc}{\vtotalc^{\prime}}                           
        \end{tikzcd}
    \end{equation*}
\end{frame}

\begin{frame}{$\vchannelc:\dfuncc_{\dtotalc} \mapsto \dfuncc_{\vtotalc}$: Stevens' Scales \cite{stevensTheoryScalesMeasurement1946}}
    \begin{table}[H]
        \begin{tabularx}{\textwidth}{|l|l|X|}\toprule
            \textbf{scale} & \textbf{group} & \textbf{constraint} \\\midrule
            nominal & permutation &  $\text{if } \delement_1 \neq \delement_2 \text{ then } \vchannel (\delement_1) \neq\vchannel(\delement_2)$\\
            ordinal &  monotonic & $\text{if } \delement_1 \leq \delement_2 \text{ then } \vchannel (\delement_1) \leq \vchannel(\delement_2)$\\
            interval &  translation &  $\vchannel (\delement + c) = \vchannel(\delement) + \vchannel(c)$ \\
            ratio &  scaling &  $\vchannel(\delement* c) = \vchannel(\delement)*\vchannel(c) $\\ \bottomrule
        \end{tabularx}
    \end{table}
\end{frame}

>>>>

                \item[Locally Trivial] {for every point $\dbasepointc \in \dbasec$, there exists an open neighborhood $\dbasepointc \in \opensetc \subseteq \dbasec$ s.t. there is a homeomorphism $\pi^{-1}(\opensetc)\xrightarrow{\equivc} \opensetc \times \dfiberc$}

@@

    \onslide*<0|handout:3>{
        \begin{equation*}
    \begin{tikzcd}[ampersand replacement =\&]
    \cgamma{\opensetgc_1}{\dtotalpullc\restriction_{\opensetgc_1}} 
    \arrow[dd, "\iota^*"', hook, color=set] 
    \arrow[rrrr, "\vartistc_{\opensetgc_1}", bend left, color=artist, Rightarrow] \&  \& 
    \opensetgc_1 
    \arrow[ll, "\sheafc_{\gbasec, \dtotalpullc}", color=sheaf, maps to] 
    \arrow[rr, "\sheafc_{\gbasec,\gtotalc}"', color=sheaf, maps to] \&  \& 
    \cgamma{\opensetgc_1}{\gtotalc\restriction_{\opensetgc_1}} 
    \arrow[dd, "\iota^*", hook', color=set] \\
    {} 
    \arrow[rrrr, dotted, color=artist, Rightarrow] \&\&\&\& {} \\
    \cgamma{\opensetgc_2}{\dtotalpullc\restriction_{\opensetgc_2}} 
    \arrow[rrrr, "\vartistc_{\opensetgc_2}"', bend right, color=artist, Rightarrow] \&  \& 
    \opensetgc_2 
    \arrow[ll, "\sheafc_{\gbasec,\dtotalpullc}"', color=sheaf, maps to] 
    \arrow[rr, "\sheafc_{\gbasec, \gtotalc}", color=sheaf, maps to] 
    \arrow[uu, "\iota" description, hook, color=base] \& \& 
    \cgamma{\opensetgc_2}{\gtotalc\restriction_{\opensetgc_2}}   
    \end{tikzcd}
        \end{equation*}}    
    \onslide<0|handout:1>{
        \begin{equation*}
        \textcolor{nattran}{Nat}_{\opensetgc}(\textcolor{functor}{\vindexpull}\sheafc_{\dbasec, \dtotalc}, \sheafc_{\gbasec, \gtotalc}) = 
    \textcolor{nattran}{Nat}_{\opensetc}(\sheafc_{\dbasec, \dtotalc}, \textcolor{functor}{\vindexpush}\sheafc_{\gbasec, \gtotalc})
        \end{equation*}
    }
    \onslide<0|handout:4>{
        \begin{alertblock}{pull data section \dsectionc\ over graphic space $\gbasepointc \in \gbasec$}
            \begin{equation*}
                \vindexpullc\dsectionc(\gbasepointc) = \dsectionc(\vindexc(\gbasepointc)) = \dsectionc(\dbasepointc)
            \end{equation*}
        \end{alertblock}
        \begin{alertblock}{push graphic \gsectionc\ section over data space $\dbasepointc \in \dbasec$}
            \begin{equation*}
                \vindexpushc\gsectionc(\dbasepointc) = \gsectionc\restriction_{\vindexprec(\dbasepointc)} = \gsectionc(\gbasepointc) \forall \gbasepointc \in \vindexprec(\dbasepointc)
            \end{equation*}
        \end{alertblock}
        }
\end{frame}

@@

\subsection{Equivariance}

\begin{frame}{Transform Data}
    \begin{block}{Fiber Bundle Category}
        \begin{description}[style=newline]
            \item[object] $\dfiberc \hookrightarrow \dtotalc \xrightarrow{\pi} \dbasec$
            \item[morphisms] $\dfuncc: \dtotalc \rightarrow \dtotalc$ 
        \end{description}
    \end{block}
    \begin{block}{Fiber Category}
        The fiber $\dfiberc$ is the sole object of an arbitrary category $\mathcal{C}$.
        The morphisms on the fiber are $Hom(\dfiberc, \dfiberc)$
    \end{block}

@@

\begin{frame}{Checking if \vartistc\ is equivariant}
    \begin{equation*}
        \begin{tikzcd}[ampersand replacement=\&, row sep=huge]
            \cgamma{\opensetc}{\dtotalc\restriction_{\opensetc}} 
            \arrow[rr, "\vartistc", Rightarrow, color=artist] \&  \& 
            \cgamma{\opensetgc}{\gtotalc\restriction_{\opensetgc}} 
            \arrow[rrd, "\delta"'] 
            \arrow[rr, "render"] \&  \& visualization 
            \arrow[d, "measure" description] \\ 
            \&  \&  \&  \& M
            \end{tikzcd}
    \end{equation*}
    \begin{alertblock}{Visual Measurement $\delta$}
        \begin{equation}
            \delta: \cgamma{\opensetgc}{\gtotalc\restriction_{\opensetgc}} \rightarrow M
        \end{equation}
        $M$ is a measurable component of the rendered visual element, e.g. color, position, shape, texture
    \end{alertblock}
\end{frame}

@@

\begin{frame}{Data to Visual Transformation: $\vchannelc: \dfiberc_{\dbasepointc} \mapsto \vfiberc_{\dbasepointc}$}
    \begin{columns}
    \column{.5\textwidth}
    \begin{equation*}
        \begin{tikzcd}[ampersand replacement=\&]
        \dtotalc 
        \arrow[rr, "\vchannelc_{\dbasec}", color=artist] 
        \arrow[rd, "\pi" description, dotted] 
        \arrow[ddd, "\dfuncc_{\dtotalc}"', color=action] 
        \& \& 
        \vtotalc 
        \arrow[ld, "\pi" description, dotted] 
        \arrow[ddd, "\dfuncc_{\vtotalc}", color=action] \\
        \& \dbasec \&  \\
        \& \dbasec^{\prime} 
        \arrow[u, "\dfunchc" description, color=action] \& \\
        \dfuncpullc\dtotalc 
        \arrow[ru, "\pi" description, dotted] 
        \arrow[rr, "\vchannel_{\dbasec}"', color=artist] 
        \& \& 
        \dfuncpullc\dtotalc 
        \arrow[lu, "\pi" description, dotted]
        \end{tikzcd}
    \end{equation*}
    \column{.5\textwidth} 
    \begin{equation}
    \begin{tikzcd}[ampersand replacement=\&, row sep=huge]
        \dfiberc_{\dbasepointc} 
        \arrow[rr, "\vchannelc_{\dtotalc} ", maps to, color=artist] 
        \arrow[rrdd, "{\vchannelc_{\dtotalc,\vtotalc}}" description, dashed, maps to, color=artist] 
        \&  \& 
        \vfiberc_{\dbasepointc}\coloneqq {\dfiberc_{\dbasepointc}}^{\vtotalc} \arrow[dd, "\vchannelc_{\vtotalc}", maps to, color=artist] \\
        \& \& \\
        \&  \& {\vfiberc_{\dbasepointc}}^{\vtotalc}
        \end{tikzcd}
    \end{equation}
    \end{columns}
    \begin{alertblock}{equivariance} 
       $\vchannelc: \dfuncc_{\dtotalc} \rightarrow \dfuncc_{\vtotalc}$ is a functor such that 
       \begin{description}
           \item[equivariance] {$\vchannelc(\dfuncc(\dsectionc(\dfunchc_{\dtotalc}^{-1}(\dbasepointc)))) = \dfuncc_{\vtotalc}(\vchannelc(\dsectionc(\dfunchc_{\vtotalc}^{-1}(\dbasepointc))))$\\$\dfunchc_{\dtotalc}(\dbasepointc^{\prime}) = \dfunchc_{\vtotalc}(\dbasepointc^{\prime})$}
           \item[continuity] $\lim\limits_{x\to \dbasepointc}(\vchannelc(\dsectionc(x))) = \vchannelc(\dsectionc(\dbasepointc))$ for all $\dbasepointc \in \dbasec$ 
       \end{description}
\end{alertblock}
\end{frame}

\begin{frame}{$\vchannelc:\dfuncc_{\dtotalc} \rightarrow \dfuncc_{\vtotalc}$: Stevens' Scales \cite{stevensTheoryScalesMeasurement1946}}
    \begin{table}[H]
        \begin{tabularx}{\textwidth}{|l|l|X|}\toprule
            \textbf{scale} & \textbf{group} & \textbf{constraint} \\\midrule
            nominal & permutation &  $\text{if } \delement_1 \neq \delement_2 \text{ then } \vchannel (\delement_1) \neq\vchannel(\delement_2)$\\
            ordinal &  monotonic & $\text{if } \delement_1 \leq \delement_2 \text{ then } \vchannel (\delement_1) \leq \vchannel(\delement_2)$\\
            interval &  translation &  $\vchannel (\delement + c) = \vchannel(\delement) + \vchannel(c)$ \\
            ratio &  scaling &  $\vchannel(\delement* c) = \vchannel(\delement)*\vchannel(c) $\\ \bottomrule
        \end{tabularx}
    \end{table}
\end{frame}
